DOM Review Summary

### 2024-03-17 Analysis/ReviewSummary/ReviewSummary.qmd
tweaks to study species
changed highlighting for study taxa categories

species_taxaTable <-species_clean |>
  separate_rows(Taxa_Category, sep = ", ") |>
  mutate(Total = length(unique(ID_clean))) |>
  select(Taxa_Category, ID_clean, Total) |>
  distinct() |>
  summarise(Articles = n(), 
            Proportion = round(Articles/mean(Total), 2),
            .by = Taxa_Category) |>
  arrange(-Articles) |>
  rename(Taxa = Taxa_Category)
```

@@

  ggplot() +
  geom_col(aes(x = Articles, y = Taxa, fill = Taxa)) +
  scale_fill_manual(limits = c("Bird", "Threatened", "Mammal", 
                               "Herptile", "Invasive", "Invertebrate",
                               "Lichen"),
                    values = c("darkslategrey", "firebrick4", "darkslategrey", 
                               "darkslategrey", "cyan4", "darkslategrey", 
                               "darkslategrey")) +
  theme(legend.position = "none") +
  labs(title = "Modelled taxa", y = "", 
       x = "number of articles")

@@

>>>>

species_taxaTable <-species_clean |>
  separate_rows(Taxa_Category, sep = ", ") |>
  mutate(Total = length(unique(ID_clean))) |>
  select(Taxa_Category, ID_clean, Total) |>
  distinct() |>
  summarise(Articles = n(), 
            Percentage = round(Articles/mean(Total), 2)*100,
            .by = Taxa_Category) |>
  arrange(-Articles) |>
  rename(Taxa = Taxa_Category)
```

@@

  ggplot() +
  geom_col(aes(x = Percentage, y = Taxa, fill = Taxa)) +
  scale_fill_manual(limits = c("Bird", "Threatened", "Mammal", 
                               "Herptile", "Invasive", "Invertebrate",
                               "Lichen"),
                    values = c("darkslategrey", "darkorange4", "darkslategrey", 
                               "darkslategrey", "darkorange4", "darkslategrey", 
                               "darkslategrey")) +
  theme(legend.position = "none") +
  xlim(c(0,50)) +
  labs(title = "Modelled taxa", 
       subtitle = "Multiple categories per article permitted",
       y = "", x = "Percentage of articles")

@@

```{r DataCollection_clean}
#| echo: false
